MS Technical Paper: \\ Placement Algorithms for Heterogenous FPGAs

### 2025-03-27 latex/paper/paper.tex
yea

% \begin{multicols}{2}
\section{Abstract}
    fdsafdsafdsa.

@@

% \end{multicols}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/hierarchy.png}
    \caption{Architecture Hierarchy of a Xilinx FPGA}\label{fig:hierarchy}
\end{figure*}

% \begin{multicols}{2}
\section{Xilinx 7-Series Architecture}
    Before any work can be done on a placer, one must understand the objects being placed and the structure of the medium in which those objects are placed. 
    Figure~\ref{fig:hierarchy} illustrates the architectural hierarchy of a Xilinx FPGA. 
    At its most basic level, an FPGA is a vast physical array of replicated atomic components known as Basic Elements of Logic (BELs).
    These BELs, which include programmable lookup tables (LUTs), flip flops (FFs), and programmable interconnects, form the fundamental building blocks for custom digital circuit implementations on FPGAs.

@@

% \end{multicols}
\end{document}

>>>>

\section{Abstract}
    fdsafdsafdsa.

@@

\section{Brief History of FPGA Architecture}
    \begin{figure}
        \centering
        \includegraphics[width=7.0cm]{figures/pal_2.png}
        \caption{PAL architecture with 5 inputs, 8 programmable AND gates and 4 fixed OR gates}
        \label{fig:pla}
        % https://www.electronics-tutorial.net/Programmable-Logic-Device-Architectures/Programmable-Logic-Devices/Programmable-Array-Logic-PAL/
        % https://www.naukri.com/code360/library/difference-between-pla-and-pal 
    \end{figure}

    Before any work can be done on a placer, one must understand the objects being placed and the structure of the medium in which those objects are placed.

    Configurable logic devices have undergone significant evolution over the last four decades.
    The journey began with simple devices like Programmable Logic Array (PLA), which came if the form of logic gates arranged in a "programmable-OR, programmable-AND" plane, used to implement a "sum-of-products" logic equation for each of the outputs in terms of the inputs via programmable fuses. 
    Around the same time came the redundantly named Programmable Array Logic (PAL), which simplified the PLA by fixing the OR gates, resulting in a "fixed-OR, programmable-AND" plane, which sacrificed some flexibility to simplify its manufacture and broaden its applications.

    \begin{figure}
        \centering
        \includegraphics[width=7.0cm]{figures/cpld.png}
        \caption{CPLD architecture with 4 CLBs}
        \label{fig:cpld}
        % https://www.electronics-tutorial.net/Programmable-Logic-Device-Architectures/CPLD/Complex-Programmable-Logic-Device-CPLDs/
    \end{figure}

    Then came the Complex Programmable Logic Device (CPLD), which came as an array of Configurable Logic Blocks (CLBs) stitched together by interconnection wires.
    These CLBs usually took the form of modified PAL blocks, which contained the PAL itself and some macrocells including flip-flops, multiplexers, and tri-state buffers.
    The CPLD was essentially an array of PALs interconnected by a programmable switch matrix and could be programmed via a hardware description language (HDL) like VHDL.

    \begin{figure}
        \centering
        \includegraphics[width=7.0cm]{figures/fpga.png}
        \caption{Island-style FPGA architecture with 16 CLBs}
        \label{fig:fpga}
        % https://www.electronics-tutorial.net/Programmable-Logic-Device-Architectures/FPGA/Field-programmable-gate-array-FPGA/
    \end{figure}

\section{Xilinx 7-Series Architecture}

    \begin{figure*}
        \centering
        \includegraphics[width=\textwidth]{figures/hierarchy.png}
        \caption{Architecture Hierarchy of a Xilinx FPGA}
        \label{fig:hierarchy}
    \end{figure*}

    Figure~\ref{fig:hierarchy} illustrates the architectural hierarchy of a Xilinx FPGA. 
    At its most basic level, an FPGA is a vast physical array of replicated atomic components known as Basic Elements of Logic (BELs).
    These BELs, which include programmable lookup tables (LUTs), flip flops (FFs), and programmable interconnects, form the fundamental building blocks for custom digital circuit implementations on FPGAs.

@@

\end{document}
